\vspace{-1cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2016-01-26 write_up/cricket.tex
viva dotplots

\begin{document}
\title{\vspace{-.5cm}\normalsize{Fairly Random: Impact of Winning the Toss on the Probability of Winning\footnote{You can find the scripts used to scrape the data, the final data set, and scripts used for analysis at: \href{https://github.com/dwillis/cricket-stats}{https://github.com/dwillis/cricket-stats}.}\vspace{.5cm}}}
\author{\normalsize{Gaurav Sood}\\\href{mailto:gsood07@gmail.com}{\small{gsood07@gmail.com}} \and \normalsize{Derek Willis}\\\href{mailto:dwillis@gmail.com}{\small{dwillis@gmail.com}}}
\date{\vspace{.5cm}\normalsize{\today}}
\maketitle
\doublespacing

>>>>

\begin{document}
\title{\vspace{-.5cm}\normalsize{Fairly Random: The Impact of Winning the Toss on the Probability of Winning\footnote{You can find the scripts used to scrape the data, the final data set, and scripts used for analysis at: \href{https://github.com/dwillis/cricket-stats}{https://github.com/dwillis/cricket-stats}.}\vspace{.5cm}}}
\author{\normalsize{Gaurav Sood}\\\href{mailto:gsood07@gmail.com}{\small{gsood07@gmail.com}} \and \normalsize{Derek Willis}\\\href{mailto:dwillis@gmail.com}{\small{dwillis@gmail.com}}}
\date{\vspace{.5cm}\normalsize{\today}}
\maketitle
\doublespacing
